Holomorphic field theories and higher algebra

### 2023-01-16 draft.tex
hiding and removing comments in sd section

We wish to study a holomorphic analog of supersymmetric chromodynamics.
We will call the relevant theory {\it QCD}, following convention, even though it is classical and not yet quantum.
We will specialize $G = SU(N)$ and so $G_\CC = SL(N)$.
The matter fields will consist of two types: quarks and antiquarks.
Let $\underline{N}$ denote the {\em fundamental} (or defining) representation of $SL(N)$,
so $\underline{N} = \CC^N$ with its natural left action.
\owen{That's kind of crappy notation. Let's discuss.}
\brian{Does it help us much? Or are you trying to use this to disambiguate what $\CC^N$ means.}

@@

\owen{Do we want $F > N+1$? The physicists break things into several cases. In particular, I think the moduli is unchanged under quantization only if $F$ is big enough relative to $N$ and $\check{N}$.}
\brian{I expect we want a similar condition, but I was never able to understand how that appears at the level of factorization algebras.}

@@

Now such a field theory $\cT$ on $\RR^n$ has a space of solutions $\Sol_\cT(\RR^n)$ to its equations of motion.
A {\em classical vacuum} for the theory is a solution that is translation-invariant,
i.e., a constant solution.
As the solutions $\Sol(\RR^n)$ is a derived stack (at least if you adhere to the perspective we've advocated here), there is a derived stack of classical vacua
\[
\cM_{\rm vac}(\cT) = \Sol_\cT(\RR^n)^{\RR^n}
\]
given by the substack of constant solutions.
We call it the {\em moduli stack of classical vacua} for the theory~$\cT$.

@@

\begin{rmk}\label{sols vs states}
The physicists' focus on the moduli space is not unreasonable:
one must make measurements --- i.e., evaluate functions --- to identify the state of a physical system.
The moduli space captures what can be seen by measurements (notably here, the ``vacuum expectation values'' of different vacua).
In other words, the possible classical states --- viewed as multiplicative linear functionals on the algebra of observables --- are parametrized by the underlying affine scheme of the derived moduli stack.
On the other hand, the moduli stack knows each orbit, which provides a distinct solution to the equations of motion,
and hence records much more about the classical theory; 
the space cannot distinguish between some vacua because it collapses orbits.
Moreover, the stack encodes much more data about the theory near each vacuum.
For instance, it remembers ``enhanced symmetries'' (such as the residual gauge fields) at each vacuum.
\end{rmk}

@@

This result tells us that, over the stable locus, the observables of a holomorphic QCD theory agree with a sheaf of two-dimensional chiral differential operators, as discussed in \owen{reference section of this paper}.
\owen{Do we see a WZ term? That often shows up in chiral symmetry breaking. It would be reminiscent of our $ch_2$ stuff in lower dimensions.}
\brian{that's a great question}

@@

Let's first consider the electric side, 
which can be seen as two-dimensional holomorphic BF theory to a complex two-dimensional $\beta\gamma$ system.
The $T^2$ compactification of the $\beta\gamma$ system with target $\C^{NF}$ is the topological B-model theory whose target is the formal double loop space $L^2\C^{NF}$. 
The algebra of functions of this target space is $\cO(\C^{NF}) ((z))((w))$, 
where $z,w$ are formal loop parameters which we imagine as describing the winding of the two circles we have compactified. 
The dimensional reduction simply picks out the constant modes along each circle, so we find a linear topological B-model with target $\C^{NF}$.
Similarly, the dimensional reduction of holomorphic BF theory is topological BF theory (which is a stacky version of the B-model whose target is the classifying space $BGL(N)$).
In sum, the dimensional reduction of the electric holomorphic QCD is the topological B-model whose target is the stack $\C^{NF} / GL(N)$.
As a derived mapping space, the moduli of solutions is given by
\beqn
{\rm Map}\left(\RR^2, T^*[1] \C^{NF} / GL(N)\right) .
\eeqn
The factorization algebra of observables obtained from reduction encodes the $E_2$ algebra of (holomorphic) polyvector fields on the stack~$\C^{NF} / GL(N)$.

On the magnetic side the reduction is similar, except this time we must take into account the superpotential. 
What results is a Landau--Ginzburg B-model whose target is the stack
\beqn
\C^{(F-N)F} / GL(F-N) \times \C^{F^2} .
\eeqn
The first factor comes from the reduction of the dual quarks coupled to the dual gauge theory, and the second factor comes from the reduction of the mesons. 
The potential of the Landau--Ginzburg model is given by the same expression $\check{W}$ as in~\eqref{eqn:checkW}.

@@

\begin{conj}
There is an equivalence of the following $E_2$ algebras:
\begin{itemize} 
\item (electric) the $E_2$ algebra of polyvector fields on the stack $\C^{NF} / GL(N)$, and 
\item (magnetic) the $E_2$ algebra that results from deforming the $E_2$ algebra of polyvector fields on the stack $\C^{(F-N)F} / GL(F-N) \times \C^{F^2}$ by the differential $\{\check{W},-\}$ where $\{-,-\}$ is the Schouten bracket.
\end{itemize}
\end{conj}

>>>>

We wish to study a holomorphic analog of supersymmetric chromodynamics.
We will call the relevant theory {\it QCD}, following convention, even though it is classical and not yet quantum.
We will specialize $G = SU(N)$ and so $G_\CC = SL(N)$.
The matter fields will consist of two types: quarks and antiquarks.
Let $\underline{N}$ denote the {\em fundamental} (or defining) representation of $SL(N)$,
so $\underline{N} = \CC^N$ with its natural left action.

@@

@@

Now such a field theory $\cT$ on $\RR^n$ has a space of solutions $\Sol_\cT(\RR^n)$ to its equations of motion.
A {\em classical vacuum} for the theory is a solution that is translation-invariant,
i.e., a constant solution.
As the solutions $\Sol(\RR^n)$ is a derived stack (at least if you adhere to the perspective we've advocated here), there is a derived stack of classical vacua
\[
\cM_{\rm vac}(\cT) = \Sol_\cT(\RR^n)^{\RR^n}
\]
given by the substack of constant solutions.
We call it the {\em moduli stack of classical vacuum solutions} for the theory~$\cT$.

@@

\begin{rmk}\label{sols vs states}
The physicists' focus on the moduli space is quite reasonable:
one must make measurements --- i.e., evaluate functions --- to identify the state of a physical system.
The moduli space captures what can be seen by measurements (here, the ``vacuum expectation values'' of different vacua).
In other words, the possible classical states --- viewed as multiplicative linear functionals on the algebra of observables --- are parametrized by an affine scheme underlying the derived moduli stack.
On the other hand, the moduli stack knows each orbit, which provides a distinct solution to the equations of motion,
and hence records much more about the classical theory.
By contrast, the space cannot distinguish between some vacua because it collapses orbits.
Moreover, the stack encodes much more data about the theory near each vacuum.
For instance, it remembers ``enhanced symmetries'' (such as the residual gauge fields) at each vacuum.
\end{rmk}

@@

This result tells us that, over the stable locus, the observables of a holomorphic QCD theory agree with a sheaf of two-dimensional chiral differential operators, as discussed in Section~\owen{reference section of this paper}.
%\owen{Do we see a WZ term? That often shows up in chiral symmetry breaking. It would be reminiscent of our $ch_2$ stuff in lower dimensions.}
%\brian{that's a great question}

@@

Let's first consider the electric side, 
which can be seen as two-dimensional holomorphic BF theory to a complex two-dimensional $\beta\gamma$ system.
The $T^2$ compactification of the $\beta\gamma$ system with target $\C^{NF}$ is the topological B-model theory whose target is the formal double loop space $L^2\C^{NF}$. 
The algebra of functions of this target space is $\cO(\C^{NF}) ((z))((w))$, 
where $z,w$ are formal loop parameters which we imagine as describing the winding of the two circles we have compactified. 
The dimensional reduction simply picks out the constant modes along each circle, so we find a linear topological B-model with target $\C^{NF}$.
Similarly, the dimensional reduction of holomorphic BF theory is topological BF theory (which is a stacky version of the B-model whose target is the classifying space $BGL(N)$).
In sum, the dimensional reduction of the electric holomorphic QCD is the topological B-model whose target is the stack $\C^{NF} / GL(N)$.
As a derived mapping space, the moduli of solutions is given by
\beqn
{\rm Map}\left(\RR^2, T^*[1] \left[ \C^{NF} / GL(N)\right]\right) .
\eeqn
The factorization algebra of observables obtained from reduction encodes the $E_2$ algebra of (holomorphic) polyvector fields on the stack~$\C^{NF} / GL(N)$.

On the magnetic side the reduction is similar, except this time we must take into account the superpotential. 
What results is a Landau--Ginzburg B-model whose target is the stack
\beqn
\left[\C^{(F-N)F} / GL(F-N) \right] \times \C^{F^2} .
\eeqn
The first factor comes from the reduction of the dual quarks coupled to the dual gauge theory, and the second factor comes from the reduction of the mesons. 
The potential of the Landau--Ginzburg model is given by the same expression $\check{W}$ as in~\eqref{eqn:checkW}.

@@

\begin{conj}
There is an equivalence of the following $E_2$ algebras:
\begin{itemize} 
\item (electric) the $E_2$ algebra of polyvector fields on the stack $[\C^{NF} / GL(N)]$, and 
\item (magnetic) the $E_2$ algebra that results from deforming the $E_2$ algebra of polyvector fields on the stack $[\C^{(F-N)F} / GL(F-N)] \times \C^{F^2}$ by the differential $\{\check{W},-\}$ where $\{-,-\}$ is the Schouten bracket.
\end{itemize}
\end{conj}
